Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-19 ms.tex
still describing error budget

% mention that all of this assumes that residual CMB dipole
% and other low order-corrections are negligible at 857 GHz

@@

This error budget is modeled after \cite{planckdust} Equation 7, but with some 
modifications and additions. The first term accounts for the multiplicative 
uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
Table 11 of \cite{planckcalib}. The second term is intended to represent a 
typical uncertainty due to the subtraction of the \verb|SMICA| CMB model. The 
analogous term in \cite{planckdust} Equation 7 is 
($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. an uncertainty proportional to 
the CMB model amplitude in each pixel. Because this term's spatial dependence 
has the potential to imprint the CMB anisotropies on the derived parameters, we
have chosen to replace \verb|SMICA|($p$) with a spatially constant, RMS value 
for the CMB amplitude, $\sigma_{CMB}$. Table \ref{table:offs} lists the adopted
values of $\sigma_{CMB}$. $\delta O_{\nu_i}$ represents the uncertainty in the 
band $\nu_i$ zero level offset, and the values of $\delta O_{\nu_i}$ can be 
read off from the second column of Table \ref{table:offs}. $n_{\nu_i}$ 
represents the instrumental noise in the pixel of interest, and is taken to be 
the square root of the \verb|ii_cov| parameter that accompanies each 
\PLANCK~intensity map. The next term accounts for the uncertainty on the 
CO emission correction, with $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$
(see $\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).

@@

>>>>

@@

This error budget is modeled after \cite{planckdust} Equation 7, but with some 
modifications and additions. The first term accounts for the multiplicative 
uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
Table 11 of \cite{planckcalib}. The second term represents an uncertainty due 
to our subtraction of the \verb|SMICA| CMB model. The analogous term in 
\cite{planckdust} Equation 7 is ($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. 
an uncertainty proportional to the CMB model amplitude in each pixel. Because 
this term's spatial dependence can imprint the CMB anisotropies on the derived 
parameters, we have chosen to replace \verb|SMICA|($p$) with a spatially 
constant, RMS value for the CMB amplitude, $\sigma_{CMB}$. Table 
\ref{table:offs} lists the adopted values of $\sigma_{CMB}$. $\delta O_{\nu_i}$
represents the uncertainty in the band $\nu_i$ zero level offset, and the 
values of $\delta O_{\nu_i}$ can be read off from the second column of Table 
\ref{table:offs}. $n_{\nu_i}$ represents the instrumental noise in band 
$\nu_i$. Because using per-pixel noise estimates based on the \verb|ii_cov| 
parameter can imprint sharp-edged features of the survey pattern onto the 
derived parameters, we have adopted a conservative, spatially constant value of
$n_{\nu_i}$ for each band. Table \ref{table:offs} lists the values of 
$n_{\nu_i}$ adopted. The next term accounts for the uncertainty on the CO 
emission correction, taking $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$ 
(see $\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).

@@

% mention that each of the error terms is always rescaled properly according
% to smoothing/rebinning and relevant power spectrum
